---
title: "Homework 3"
output: html_notebook
---

| Homework 3                     |                Data Analysis with R |
| :---                           |                                ---: |
| Due by 11:59 PM on Wed Sep 13  | Business Analytics Graduate Program |
| Submit via codePost            |                 BAIS:6060 Fall 2023 |

# Instructions

Follow all of the guidelines given on prior homeworks, referring to
them as necessary. Here is an important reminder: include the required
`library(...)` commands in your notebook.

Also included with this homework is the solution for exercise #1 within
the included file `soln.Rdata`. To see this solution, execute this
command at the console: `load("soln.Rdata", soln <- new.env())`. Points
will be deducted if your solution loads or uses `soln.Rdata` explicitly.

# Exercises



## #1

Carefully review the included files `movies.txt` and `movies.csv`
(taking note of the column classes!) and then complete the following
exercises.

### (a)

Read the data correctly into `df`.

```{r}

```

### (b)

Create a new column `df$GrossRatio`, which equals the ratio of
`TotalGross` over `OpeningGross`. [Hint: For each movie, the value of
the ratio should be greater than or equal to 1.0. Do not round.]

```{r}

```

### (c)

Rename the levels of `df$Studio` according to the following table:

    "WB"        "Warner Brothers"
    "Uni."      "Universal"
    "BV"        "Buena Vista"
    "Fox"       "Fox" (i.e., no change)
    "Par."      "Paramount"
    "Sony"      "Sony" (i.e., no change)
    "MGM"       "MGM" (i.e., no change)
    "Mira."     "Miramax"

```{r}

```

### (d)

Now rename all other levels not listed in the prior exercise to "Other",
i.e., merge all those levels to "Other". [Hint: The commands

    to_keep <- c("Warner Brothers", "Universal", "Fox")
    to_merge <- setdiff(levels(df$Studio), to_keep)

    df <- mutate(df, Studio = fct_collapse(Studio, Other = to_merge))

would merge everything but "Warner Brothers", "Universal", and "Fox".
But that would merge too much. Alter the command to make sure the merge
is correct.]

```{r}

```

### (e)

Now overwrite `df$Studio` so that its levels are in alphabetical
order---except that "Other" is the last level.

```{r}

```

### (f)

Use the `cut(...)` command with options

    breaks = quantile(df$GrossRatio)

and

    include.lowest = TRUE

to create a new factor column `df$Stamina`, which groups the movies by
their `GrossRatio` quartile. Make sure the levels of `df$Stamina` are
"Weaker", "Weak", "Strong", and "Stronger" in that order, which can be
done: (i) inside the `cut` command using its `labels` option; (ii) or
using `dplyr` commands after `df$Stamaina` is created.

[Hints: If done correctly, there should be no `NA`'s in `df$Stamina`.
"Weaker" movies are those that enjoy a lot of initial interest from
audiences, but then interest dwindles relatively quickly over time
(e.g., *Avengers: Endgame*), whereas "Stronger" movies enjoy continued
audience interest over time (e.g,. *E.T.: The Extra-Terrestrial*).]

```{r}

```

## #2

The overall goal of this exercise, which is broken down into several
parts, is to determine which studio has the highest percentage of
"Stronger" movies among its own movie releases. [Hint: The answer should
be Miramax.]

### (a)

In a new object `part_a`, save a summary of `df`, which counts the
number of records in each group defined by the two columns `Studio` and
`Stamina`. Call the summary column `number`. After `part_a` is created,
also execute the command `df <- ungroup(df)` to remove any groupings on
`df` that you created.

```{r}

```

### (b)

Copy `part_a` to a new object `part_b`, and then group `part_b`
by `Studio`. Next use the `mutate(...)` command to create a new
column in `part_b`, called `percent`, which equals the calculation
`number/sum(number)`, where `number` refers to the column in `part_b`,
which came from `part_a`.

```{r}

```

### (c)

Finally, create a table from `part_b`, which has `Studio` as the rows,
`Stamina` as the columns, and values from the `percent` column. Save the
result in an object called `part_c`.

```{r}


```

## #3

In the console, the command

    as.factor(10*floor(as.numeric(format(df$OpeningDate, "%Y")) / 10))

creates a factor vector, which shows the decade each movie was released,
e.g., "1980" stands for the 1980's, "1990" stands for the 1990's, etc.
Incorporating this idea, use a single command with the pipe operator to
create a table called `num_3`, which has `Studio` as the rows and the
decade as the columns and which shows the total number of movies in each
studio-decade pair. Do not overwrite `df` during this process.

```{r}


```

## #4

Undo the grouping on `df`, and then use `dplyr` functions and the pipe
operator to create a single command (probably split over several lines
in your notebook) that creates a data frame called `top_movies` with the
following structure and content (please no extra columns):

    Title | OpeningDate | TotalGross | GrossRatio
    ---------------------------------------------
     ...  |     ...     |    ...     |    ...
     ...  |     ...     |    ...     |    ...


- The rows in `top_movies` correspond to the top-10 movies in terms of
having the highest values of `GrossRatio`, among all movies with at
least $100,000,000 in total gross and at least 1,000 opening theaters.

- The movies are sorted by `OpeningDate`, newest to oldest.

[Hint: In addition to the main `dplyr` commands taught in the
module, try using the `slice_max(...)` function as described here:
https://dplyr.tidyverse.org/reference/slice.html. The `slice_max`
function was also used in the Module 3 lesson. To get started, try
something like `df %>% slice_max(GrossRatio, n = 10)` in the console.
Partial credit will be given if the correct answer is gotten using
techniques different than those specified.]

```{r}

```
